Hunting experience and prey behaviour shape individual foraging specialisation in a predator-prey videogame

### 2023-01-31 manuscript/Chapter2-SupInfo.Rmd
updated supmat

---
title: "Hunting experience and prey variability jointly shape individual foraging specialisation in a predator-prey videogame"
output: 
  word_document:
    reference_docx: Chapter2-styles.docx
    fig_caption: yes
bibliography: references.bib
csl: e-letters.csl
---

@@

```{r tableS1, eval = FALSE, ft.align = "left"}

tab1 <- readRDS(here::here("outputs", "05_outputs_tables", "05_table1.rds"))

set_caption(
  tab1,
  caption = "Posterior mean values, standard errors, and 95% credible intervals for the GAMM with a common global smoother. The values are presented on the logit scale.",
  style = "Table Caption"
)

>>>>

---
title: "Hunting experience and prey behaviour shape individual foraging specialisation in a predator-prey videogame"
output: 
  word_document:
    reference_docx: Chapter2-styles.docx
    fig_caption: yes
bibliography: references.bib
csl: e-letters.csl
---

@@
